Predictors of frog survival following translocations - supplemental analyses

### 2024-04-10 code/translocation_survival_analysis_supp.Rmd

d1 %>% 
  mutate(period = factor(period, levels = c("before", "after"))) %>% 
  filter(interval < 2) %>% 
  ggplot(aes(x = period, y = log10(bd_load + 1))) +
    geom_boxplot() + 
    labs(x = "Period (relative to translocation)", y = (expression(Bd~load~(log["10"]~copies+1)))) +
    coord_cartesian(ylim = c(-0.5, NA)) +
    facet_grid(. ~ site_id1) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
          strip.text.x = element_text(size = 8),
          panel.grid = element_blank()) +
    geom_text(data = smplsize, aes(x = period, y = -0.4, label = n), size = 2.2, vjust = 1)

>>>>

d1 %>% 
  mutate(period = factor(period, levels = c("before", "after"))) %>% 
  filter(interval < 2) %>% 
  ggplot(aes(x = period, y = log10(bd_load + 1))) +
    geom_boxplot() + 
    labs(x = "Period (relative to translocation)", y = (expression(Bd~load~(log["10"]~copies+1)))) +
    coord_cartesian(ylim = c(-0.5, NA)) +
    facet_grid(. ~ site_id1) +
    geom_hline(yintercept = 5.78, color = "red", linetype = 2) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
          strip.text.x = element_text(size = 8),
          panel.grid = element_blank()) +
    geom_text(data = smplsize, aes(x = period, y = -0.4, label = n), size = 2.2, vjust = 1)
